---
title: Supplementary materials for "Multiplicity adjustments for the Dunnett procedure
  under heteroscedasticity"
author: ''
date: "6/5/2023"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document illustrates the example in Section 6 of "Multiplicity adjustments
for the Dunnett procedure under heteroscedasticity" by Tamhane and Xi. The
birthweight dataset is available in the R package multcomp. R code to reproduce
this document can be found at \url{https://github.com/xidongdxi/dunnett}.

## Prepare summary input data for Table 3
```{r data, echo=TRUE}
library(multcomp)
data("litter")
data <- subset(litter, select = c(dose, weight))
doses <- c(0, 5, 50, 500)
tab3_input <- data.frame(dose = doses, X = NA, S2 = NA, n = NA, t = NA, nu = NA)
for (i in 1:length(doses)) {
  temp <- subset(data, dose == doses[i])
  tab3_input[i, 2] <- mean(temp$weight)
  tab3_input[i, 3] <- var(temp$weight)
  tab3_input[i, 4] <- length(temp$weight)
  if (doses[i] != 0) {
    tab3_input[i, 5] <- (tab3_input[1, 2] - tab3_input[i, 2]) / 
      sqrt(tab3_input[i, 3] / tab3_input[i, 4] + tab3_input[1, 3] / tab3_input[1, 4])
    tab3_input[i, 6] <- (tab3_input[i, 3] / tab3_input[i, 4] +
                        tab3_input[1, 3] / tab3_input[1, 4])^2 /
      (tab3_input[i, 3]^2 / tab3_input[i, 4]^2 / (tab3_input[i, 4] - 1) +
         tab3_input[1, 3]^2 / tab3_input[1, 4]^2 / (tab3_input[1, 4] - 1))
  }
  tab3_input
}
tab3_input$X <- round(tab3_input$X, 2)
tab3_input$S2 <- round(tab3_input$S2, 2)
tab3_input$t <- round(tab3_input$t, 2)
tab3_input$nu <- round(tab3_input$nu, 2)
print(tab3_input, row.names = FALSE) # Table 3, columns 1-6
```

## Check for heteroscedasticity
```{r check heteroscedasticity, echo=TRUE}
k <- length(doses) - 1
x <- tab3_input$X
s2 <- tab3_input$S2
n <- tab3_input$n
t <- tab3_input$t
nu <- tab3_input$nu
nu_0 <- sum(n) - (k + 1)
nu_0 # $\nu$
s2_0 <- sum((n - 1) * s2) / nu_0
round(s2_0, 3) # $S^2$
c_Bartlett <- 1 + 1 / 3 / k * (sum(1 / (n - 1)) - 1 / nu_0)
round(c_Bartlett, 3) # Bartlett correction factor
X2 <- (nu_0 * log(s2_0) - sum((n - 1) * log(s2))) / c_Bartlett
round(X2, 3) # Bartlett statistic $X^2$ 
# p-value for the Bartlett test
round(pchisq(X2, 3, lower.tail = F), 4)
```

## Correlation matrix for the PI method
```{r PI, echo=TRUE}
lambda <- sqrt(s2[1] / n[1] / (s2[1] / n[1] + s2[-1] / n[-1]))
round(lambda, 3) # PI estimates of the $\lambda_i$ defined in (6)

corr_PI <- matrix(0, nrow = k, ncol = k)
for(i in 1:k) {
  for (j in 1:k) {
    corr_PI[i, j] <- lambda[i] * lambda[j]
  }
}
diag(corr_PI) <- 1
round(corr_PI, 3) # PI correlation in (5)

eta <- s2[1] / n[1] / sqrt(n[1] - 1) /
  sqrt((s2[1]^2 / n[1]^2 / (n[1] - 1) + s2[-1]^2 / n[-1]^2 / (n[-1] - 1)))
round(eta, 3) # PI estimates of the $\eta_i$ in (8)

corr_U <- matrix(0, nrow = k, ncol = k)
for(i in 1:k) {
  for (j in 1:k) {
    corr_U[i, j] <- eta[i] * eta[j]
  }
}
diag(corr_U) <- 1
round(corr_U, 3) # Desired estimated correlation (10)
```

## Correlation matrix for the proposed method
```{r proposed method, echo=TRUE}
c_val <- eta^2 * nu[-1]
round(c_val, 3) # c's
d_val <- nu[-1] - c_val
round(d_val, 3) # d's
round(c_val[order(c_val)], 3) # Ordered c's
round(c(c_val[order(c_val)][1], c_val[order(c_val)][2] - c_val[order(c_val)][1],
            c_val[order(c_val)][3] - c_val[order(c_val)][2]), 3) # Ordered increments of c's
round(d_val[order(c_val)], 3) # Ordered d's

corr_U_approx <- matrix(0, nrow = k, ncol = k)
for(i in 1:k) {
  for (j in 1:k) {
    if (rank(c_val)[i] < rank(c_val)[j]) {
      corr_U_approx[i, j] <- eta[i]^2 * sqrt(nu[-1][i] / nu[-1][j])
    } else {
      corr_U_approx[i, j] <- eta[j]^2 * sqrt(nu[-1][j] / nu[-1][i])
    }
  }
}
diag(corr_U_approx) <- 1
round(corr_U_approx, 3) # Correlation matrix among the $U_i$’s using (9)
```
## Load functions for Methods 0-3
```{r location, echo=F}
folder <- "C:/Users/dxi1/OneDrive - Gilead Sciences/Paper/Dunnett/code/"
```

```{r functions, echo=TRUE}
setwd(folder)
source("functions.R")
```

## Adjusted p-values of Methods 0
```{r adjusted pvalue 0, echo=TRUE}
library(mvtnorm)
set.seed(10000)
# Method 0
time <- proc.time()
padj0 <- homo_func(x_0 = tab3_input$X[1], x = tab3_input$X[-1],
                   s2_0 = tab3_input$S2[1], s2 = tab3_input$S2[-1],
                   n_0 = tab3_input$n[1], n = tab3_input$n[-1], direction = "lower")
time0 <- c(proc.time() - time)[3]
```

## Adjusted p-values of Methods 1
```{r adjusted pvalue 1, echo=TRUE}
# Method 1
time <- proc.time()
padj1 <- ind_func(x_0 = tab3_input$X[1], x = tab3_input$X[-1],
                  s2_0 = tab3_input$S2[1], s2 = tab3_input$S2[-1],
                  n_0 = tab3_input$n[1], n = tab3_input$n[-1], direction = "lower")
time1 <- c(proc.time() - time)[3]
```

## Adjusted p-values of Methods 2
```{r adjusted pvalue 2, echo=TRUE}
# Method 2
time <- proc.time()
padj2 <- PI_func(x_0 = tab3_input$X[1], x = tab3_input$X[-1],
                 s2_0 = tab3_input$S2[1], s2 = tab3_input$S2[-1],
                 n_0 = tab3_input$n[1], n = tab3_input$n[-1], direction = "lower")
time2 <- c(proc.time() - time)[3]
```

## Adjusted p-values of Methods 3
```{r adjusted pvalue 3, echo=TRUE}
# Method 3
time <- proc.time()
padj3 <- sim_based_func(x_0 = tab3_input$X[1], x = tab3_input$X[-1],
                        s2_0 = tab3_input$S2[1], s2 = tab3_input$S2[-1],
                        n_0 = tab3_input$n[1], n = tab3_input$n[-1],
                        direction = "lower", nsim = 1e5)
time3 <- c(proc.time() - time)[3]

tab3 <- data.frame(tab3_input,
                   Padj0 = c(NA, round(padj0, 4)),
                   Padj1 = c(NA, round(padj1, 4)),
                   Padj2 = c(NA, round(padj2, 4)),
                   Padj3 = c(NA, round(padj3, 4)))
print(tab3, row.names = FALSE) # Table 3

time <- c(time0, time1, time2, time3)
names(time) <- paste0("Method", 0:3)
time # Computing time in seconds

sessionInfo()
```
