---
title: Simulations for "Multiplicity adjustments for the Dunnett procedure
  under heteroscedasticity"
author: ''
date: "6/5/2023"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document provides simulation studies in Section 5 of "Multiplicity adjustments
for the Dunnett procedure under heteroscedasticity" by Tamhane and Xi.

## Simulation function
```{r function, echo=TRUE}
setwd("/dunnett/simulation/")
source("/dunnett/functions.R")
sim <- function(x, arg) {
  mu <- unlist(arg$mu[x])
  sigma <- unlist(arg$sigma[x])
  n <- unlist(arg$n[x])
  direct <- arg$direction[x]
  nrep <- arg$nrep[x]
  alpha <- arg$alpha[x]
  k <- length(mu)
  padj0 <- padj1 <- padj2 <- padj3 <- matrix(0, nrow = nrep, ncol = k - 1)
  time0 <- time1 <- time2 <- time3 <- rep(NA, nrep)
  for(i in 1:nrep) {
    data <- data.frame(trt = rep(1:k, n), mu = rep(mu, n), resp = NA)
    muhat <- mu
    s <- sigma
    for (j in 1:k) {
      temp <- rnorm(n = n[j], mean = mu[j], sd = sigma[j])
      data$resp[data$trt == j] <- temp
      muhat[j] <- mean(temp)
      s[j] <- sqrt(sum((temp - muhat[j])^2) / (n[j] - 1))
    }
    summary <- data.frame(x = muhat, s2 = s^2, n = n)
    t <- c(NA, mu[-1])
    nu <- c(NA, mu[-1])
    for (j in 2:k) {
      t[j] <- (muhat[j] - muhat[1]) / sqrt(s[j]^2 / n[j] + s[1]^2 / n[1])
      nu[j] <- (s[j]^2 / n[j] + s[1]^2 / n[1])^2 /
        (s[j]^4 / n[j]^2 / (n[j] - 1) + s[1]^4 / n[1]^2 / (n[1] - 1))
    }
    summary <- data.frame(summary, t = t, nu = nu)
    # Method 0
    time <- proc.time()
    padj0[i, ] <- homo_func(x_0 = summary$x[1], x = summary$x[-1],
                            s2_0 = summary$s2[1], s2 = summary$s2[-1],
                            n_0 = summary$n[1], n = summary$n[-1],
                            direction = direct)
    time0 <- c(proc.time() - time)[3]
    # Method 1
    time <- proc.time()
    padj1[i, ] <- ind_func(x_0 = summary$x[1], x = summary$x[-1],
                           s2_0 = summary$s2[1], s2 = summary$s2[-1],
                           n_0 = summary$n[1], n = summary$n[-1],
                           direction = direct)
    time1 <- c(proc.time() - time)[3]
    # Method 2
    time <- proc.time()
    padj2[i, ] <- PI_func(x_0 = summary$x[1], x = summary$x[-1],
                          s2_0 = summary$s2[1], s2 = summary$s2[-1],
                          n_0 = summary$n[1], n = summary$n[-1],
                          direction = direct)
    time2 <- c(proc.time() - time)[3]
    # Method 3
    m <- 1e5
    time <- proc.time()
    padj3[i, ] <- sim_based_func(x_0 = summary$x[1], x = summary$x[-1],
                                 s2_0 = summary$s2[1], s2 = summary$s2[-1],
                                 n_0 = summary$n[1], n = summary$n[-1],
                                 direction = direct, nsim = m)
    time3 <- c(proc.time() - time)[3]
  }
  
  m0 <- m1 <- m2 <- m3 <- 0
  dec0 <- padj0 <= alpha
  dec1 <- padj1 <= alpha
  dec2 <- padj2 <= alpha
  dec3 <- padj3 <= alpha
  if (all(mu[-1] - mu[1] == 0)) {
    m0 <- mean(apply(dec0, 1, max))
    m1 <- mean(apply(dec1, 1, max))
    m2 <- mean(apply(dec2, 1, max))
    m3 <- mean(apply(dec3, 1, max))
  } else if (all(mu[-1] - mu[1] > 0)) {
    m0 <- m1 <- m2 <- m3 <- NA
  } else {
    temp <- which(mu[-1] - mu[1] == 0)
    if (length(temp) == 1) {
      m0 <- mean(dec0[, temp])
      m1 <- mean(dec1[, temp])
      m2 <- mean(dec2[, temp])
      m3 <- mean(dec3[, temp])
    } else {
      m0 <- mean(apply(dec0[, temp], 1, max))
      m1 <- mean(apply(dec1[, temp], 1, max))
      m2 <- mean(apply(dec2[, temp], 1, max))
      m3 <- mean(apply(dec3[, temp], 1, max))
    }
  }
  out <- matrix(c(mu, n, sigma^2, nrep, alpha, mean(time0), m0, mean(time1),
                  m1, mean(time2), m2, mean(time3), m3), nrow = 1)
  colnames(out) <- c(paste0("mu_", 0:(k - 1)),
                     paste0("n_", 0:(k - 1)),
                     paste0("sigma_", 0:(k - 1),".2"),
                     "nrep",
                     "alpha",
                     "time0", "m0_fwer",
                     "time1", "m1_fwer",
                     "time2", "m2_fwer",
                     "time3", "m3_fwer"
  )
  return(out)
}
```

## Simulation scenarios for two treatment groups and control
We used the nominal one-sided $\alpha=0.025$ and the total sample size $N=30$.
The following seven scenarios were considered where scenarios 1, 3, 4 and 5 were
also considered by Hasler and Hornthon (2008). For each scenario, 100,000
simulated data sets were generated for each method under the global null
hypothesis of $\mu_0=\mu_1=\mu_2=0$. For Method 3, 100,000 replicates were
generated for each simulation.

1. Balanced allocation with equal standard deviations:\
$n_0=10, n_1=10, n_2=10$ and $\sigma_0=30, \sigma_1=30, \sigma_2=30$
2. Balanced allocation with control having the largest standard deviation:\
$n_0=10, n_1=10, n_2=10$ and $\sigma_0=50, \sigma_1=10, \sigma_2=10$
3. Balanced allocation with one treatment having the largest standard
deviation:\
$n_0=10, n_1=10, n_2=10$ and $\sigma_0=10, \sigma_1=10, \sigma_2=50$
4. Unbalanced allocation with control having the smallest sample size and
standard deviation:\
$n_0=4, n_1=13, n_2=13$ and $\sigma_0=10, \sigma_1=10, \sigma_2=50$
5. Unbalanced allocation with one treatment having the smallest sample size
and the largest standard deviation:\
$n_0=13, n_1=13, n_2=4$ and $\sigma_0=10, \sigma_1=10, \sigma_2=50$
6. Unbalanced allocation with control having the smallest sample size and
the largest standard deviation:\
$n_0=4, n_1=13, n_2=13$ and $\sigma_0=50, \sigma_1=10, \sigma_2=10$
7. Unbalanced allocation with a treatment having the smallest sample size
and the smallest standard deviation:\
$n_0=13, n_1=13, n_2=4$ and $\sigma_0=50, \sigma_1=10, \sigma_2=10$

```{r scenarios two, echo=TRUE}
arg <- data.frame(mu = I(list(rep(0, 3), rep(0, 3), rep(0, 3), rep(0, 3),
                              rep(0, 3), rep(0, 3), rep(0, 3),
                              c(0, 20, 0), c(0, 20, 0), c(0, 20, 0), c(0, 20, 0),
                              c(0, 20, 0), c(0, 20, 0), c(0, 20, 0))),
                  n = I(list(rep(10, 3), rep(10, 3), rep(10, 3), c(4, 13, 13),
                           c(13, 13, 4), c(4, 13, 13),
                           c(13, 13, 4),
                           rep(10, 3), rep(10, 3), rep(10, 3), c(4, 13, 13),
                           c(13, 13, 4), c(4, 13, 13),
                           c(13, 13, 4))),
                  sigma = I(list(rep(30, 3), c(50, 10, 10), c(10, 10, 50), c(10, 10, 50),
                               c(10, 10, 50), c(50, 10, 10), c(50, 10, 10),
                               rep(30, 3), c(50, 10, 10), c(10, 10, 50), c(10, 10, 50),
                               c(10, 10, 50), c(50, 10, 10), c(50, 10, 10))),
                  direction = "lower", nrep = 1e5, alpha = 0.025)
n_arg <- nrow(arg)

# # Parallel
# library(future.apply)
# plan(cluster)
# seed <- 10000
# result <- future_lapply(1:n_arg, FUN = sim, future.seed = seed,
#                         future.packages = c("mvtnorm"), arg = arg, future.scheduling = n_arg)
# results <- as.data.frame(do.call(rbind, result))
```

### Tables 1 and 2
```{r outputs two, echo=TRUE}
results <- read.csv("/dunnett/simulation/two_treatment_groups.csv")
data_tbl1 <- subset(results, mu_1 == 0, select = -c(mu_0, mu_1, mu_2,
                                                    n_0, n_1, n_2,
                                                    sigma_0.2, sigma_1.2, sigma_2.2,
                                                    nrep, alpha,
                                                    time0, time1, time2, time3))
row.names(data_tbl1) <- 1:nrow(data_tbl1)
t(data_tbl1) # Table 1

data_tbl2 <- subset(results, mu_1 == 20, select = -c(mu_0, mu_1, mu_2,
                                                     n_0, n_1, n_2,
                                                     sigma_0.2, sigma_1.2, sigma_2.2,
                                                     nrep, alpha,
                                                     time0, time1, time2, time3))
row.names(data_tbl2) <- 1:nrow(data_tbl2)
t(data_tbl2) # Table 2

data_time <- subset(results, select = -c(mu_0, mu_1, mu_2,
                                         n_0, n_1, n_2,
                                         sigma_0.2, sigma_1.2, sigma_2.2,
                                         nrep, alpha,
                                         m0_fwer, m1_fwer, m2_fwer, m3_fwer))
round(colMeans(data_time), 4) # Mean computing time for each replication

```
## Simulation scenarios for three treatment groups and control
We used the nominal one-sided $\alpha=0.025$ and the total sample size $N=40$.
The following seven scenarios were considered. For each scenario, 100,000
simulated data sets were generated for each method under the global null
hypothesis of $\mu_0=\mu_1=\mu_2=\mu_3=0$,
under $\mu_0=\mu_2=\mu_3=0, \mu_1=20$, and
under $\mu_0=\mu_3=0, \mu_1=\mu_2=20$. For Method 3, 100,000 replicates were
generated for each simulation.

1. Balanced allocation with equal standard deviations:
$n_0=10, n_1=10, n_2=10, n_3=10$ and
$\sigma_0=30, \sigma_1=30, \sigma_2=30, \sigma_3=30$
2. Balanced allocation with control having the largest standard deviation:
$n_0=10, n_1=10, n_2=10, n_3=10$ and
$\sigma_0=50, \sigma_1=10, \sigma_2=10, \sigma_3=10$
3. Balanced allocation with one treatment having the largest standard
deviation:
$n_0=10, n_1=10, n_2=10, n_3=10$ and
$\sigma_0=10, \sigma_1=10, \sigma_2=10, \sigma_3=50$
4. Unbalanced allocation with control having the smallest sample size and
standard deviation:
$n_0=4, n_1=12, n_2=12, n_3=12$ and
$\sigma_0=10, \sigma_1=10, \sigma_2=10, \sigma_3=50$
5. Unbalanced allocation with one treatment having the smallest sample size
and the largest standard deviation:
$n_0=12, n_1=12, n_2=12, n_3=4$ and
$\sigma_0=10, \sigma_1=10, \sigma_2=10, \sigma_3=50$
6. Unbalanced allocation with control having the smallest sample size and
the largest standard deviation:
$n_0=4, n_1=12, n_2=12, n_3=12$ and
$\sigma_0=50, \sigma_1=10, \sigma_2=10, \sigma_3=10$
7. Unbalanced allocation with a treatment having the smallest sample size
and the smallest standard deviation:
$n_0=12, n_1=12, n_2=12, n_3=4$ and
$\sigma_0=50, \sigma_1=10, \sigma_2=10, \sigma_3=10$

```{r scenarios three, echo=TRUE}
arg <- data.frame(mu = I(list(rep(0, 4), rep(0, 4), rep(0, 4), rep(0, 4),
                              rep(0, 4), rep(0, 4), rep(0, 4),
                              c(0, 20, 0, 0), c(0, 20, 0, 0), c(0, 20, 0, 0),
                              c(0, 20, 0, 0), c(0, 20, 0, 0), c(0, 20, 0, 0),
                              c(0, 20, 0, 0),
                              c(0, 20, 20, 0), c(0, 20, 20, 0), c(0, 20, 20, 0),
                              c(0, 20, 20, 0), c(0, 20, 20, 0), c(0, 20, 20, 0),
                              c(0, 20, 20, 0))),
                  n = I(list(rep(10, 4), rep(10, 4), rep(10, 4), c(4, 12, 12, 12),
                           c(12, 12, 12, 4), c(4, 12, 12, 12),
                           c(12, 12, 12, 4),
                           rep(10, 4), rep(10, 4), rep(10, 4), c(4, 12, 12, 12),
                           c(12, 12, 12, 4), c(4, 12, 12, 12),
                           c(12, 12, 12, 4),
                           rep(10, 4), rep(10, 4), rep(10, 4), c(4, 12, 12, 12),
                           c(12, 12, 12, 4), c(4, 12, 12, 12),
                           c(12, 12, 12, 4))),
                  sigma = I(list(rep(30, 4), c(50, 10, 10, 10), c(10, 10, 10, 50),
                                 c(10, 10, 10, 50), c(10, 10, 10, 50),
                                 c(50, 10, 10, 10), c(50, 10, 10, 10),
                               rep(30, 4), c(50, 10, 10, 10), c(10, 10, 10, 50),
                                 c(10, 10, 10, 50), c(10, 10, 10, 50),
                               c(50, 10, 10, 10), c(50, 10, 10, 10),
                               rep(30, 4), c(50, 10, 10, 10), c(10, 10, 10, 50),
                                 c(10, 10, 10, 50), c(10, 10, 10, 50),
                               c(50, 10, 10, 10), c(50, 10, 10, 10))),
                  direction = "lower", nrep = 1e5, alpha = 0.025)
n_arg <- nrow(arg)

# # Parallel
# library(future.apply)
# plan(cluster)
# seed <- 10000
# result <- future_lapply(1:n_arg, FUN = sim, future.seed = seed,
#                         future.packages = c("mvtnorm"), arg = arg,
# future.scheduling = n_arg)
# results <- as.data.frame(do.call(rbind, result))
```

### Results for three treatment groups and control
```{r outputs three, echo=TRUE}
results <- read.csv("/dunnett/simulation/three_treatment_groups.csv")
# $\mu_0=\mu_1=\mu_2=\mu_3=0$
data_0_0_0_0 <- subset(results, mu_1 == 0 & mu_2 == 0,
                       select = -c(mu_0, mu_1, mu_2, mu_3,
                                   n_0, n_1, n_2, n_3,
                                   sigma_0.2, sigma_1.2, sigma_2.2, sigma_3.2,
                                   nrep, alpha,
                                   time0, time1, time2, time3))
row.names(data_0_0_0_0) <- 1:nrow(data_0_0_0_0)
t(data_0_0_0_0) # $\mu_0=\mu_1=\mu_2=\mu_3=0$

# $\mu_0=\mu_2=\mu_3=0, \mu_1=20$
data_0_20_0_0 <- subset(results, mu_1 == 20 & mu_2 == 0,
                        select = -c(mu_0, mu_1, mu_2, mu_3,
                                    n_0, n_1, n_2, n_3,
                                    sigma_0.2, sigma_1.2, sigma_2.2, sigma_3.2,
                                    nrep, alpha,
                                    time0, time1, time2, time3))
row.names(data_0_20_0_0) <- 1:nrow(data_0_20_0_0)
t(data_0_20_0_0) # $\mu_0=\mu_2=\mu_3=0, \mu_1=20$

# $\mu_0=\mu_3=0, \mu_1=\mu_2=20$
data_0_20_20_0 <- subset(results, mu_1 == 20 & mu_2 == 20,
                         select = -c(mu_0, mu_1, mu_2, mu_3,
                                    n_0, n_1, n_2, n_3,
                                    sigma_0.2, sigma_1.2, sigma_2.2, sigma_3.2,
                                    nrep, alpha,
                                    time0, time1, time2, time3))
row.names(data_0_20_20_0) <- 1:nrow(data_0_20_20_0)
t(data_0_20_20_0) # $\mu_0=\mu_3=0, \mu_1=\mu_2=20$

data_time <- subset(results, select = -c(mu_0, mu_1, mu_2, mu_3,
                                         n_0, n_1, n_2, n_3,
                                         sigma_0.2, sigma_1.2, sigma_2.2, sigma_3.2,
                                         nrep, alpha, 
                                         m0_fwer, m1_fwer, m2_fwer, m3_fwer))
round(colMeans(data_time), 4) # Mean computing time for each replication

```

## Simulation scenarios for four treatment groups and control
We used the nominal one-sided $\alpha=0.025$ and the total sample size $N=50$.
The following seven scenarios were considered. For each scenario, 100,000
simulated data sets were generated for each method under the global null
hypothesis of $\mu_0=\mu_1=\mu_2=\mu_3=\mu_4=0$,
under $\mu_0=\mu_2=\mu_3=\mu_4=0, \mu_1=20$,
under $\mu_0=\mu_3=\mu_4=0, \mu_1=\mu_2=20$, and under
under $\mu_0=\mu_4=0, \mu_1=\mu_2=\mu_3=20$. For Method 3, 100,000 replicates were
generated for each simulation.

1. Balanced allocation with equal standard deviations:
$n_0=10, n_1=10, n_2=10, n_3=10, n_4=10$ and
$\sigma_0=30, \sigma_1=30, \sigma_2=30, \sigma_3=30, \sigma_4=30$
2. Balanced allocation with control having the largest standard deviation:
$n_0=10, n_1=10, n_2=10, n_3=10, n_4=10$ and
$\sigma_0=50, \sigma_1=10, \sigma_2=10, \sigma_3=10, \sigma_4=10$
3. Balanced allocation with one treatment having the largest standard
deviation:
$n_0=10, n_1=10, n_2=10, n_3=10, n_4=10$ and
$\sigma_0=10, \sigma_1=10, \sigma_2=10, \sigma_3=10, \sigma_4=50$
4. Unbalanced allocation with control having the smallest sample size and
standard deviation:
$n_0=6, n_1=11, n_2=11, n_3=11, n_4=11$ and
$\sigma_0=10, \sigma_1=10, \sigma_2=10, \sigma_3=10, \sigma_4=50$
5. Unbalanced allocation with one treatment having the smallest sample size
and the largest standard deviation:
$n_0=11, n_1=11, n_2=11, n_3=11, n_4=6$ and
$\sigma_0=10, \sigma_1=10, \sigma_2=10, \sigma_3=10, \sigma_4=50$
6. Unbalanced allocation with control having the smallest sample size and
the largest standard deviation:
$n_0=6, n_1=11, n_2=11, n_3=11, n_4=11$ and
$\sigma_0=50, \sigma_1=10, \sigma_2=10, \sigma_3=10, \sigma_4=10$
7. Unbalanced allocation with a treatment having the smallest sample size
and the smallest standard deviation:
$n_0=11, n_1=11, n_2=11, n_3=11, n_4=6$ and
$\sigma_0=50, \sigma_1=10, \sigma_2=10, \sigma_3=10, \sigma_4=10$

```{r scenarios four, echo=TRUE}
arg <- data.frame(mu = I(list(rep(0, 5), rep(0, 5), rep(0, 5), rep(0, 5),
                             rep(0, 5), rep(0, 5), rep(0, 5),
                             c(0, 20, 0, 0, 0), c(0, 20, 0, 0, 0), c(0, 20, 0, 0, 0),
                             c(0, 20, 0, 0, 0), c(0, 20, 0, 0, 0), c(0, 20, 0, 0, 0),
                             c(0, 20, 0, 0, 0),
                             c(0, 20, 20, 0, 0), c(0, 20, 20, 0, 0), c(0, 20, 20, 0, 0),
                             c(0, 20, 20, 0, 0), c(0, 20, 20, 0, 0), c(0, 20, 20, 0, 0),
                             c(0, 20, 20, 0, 0),
                             c(0, 20, 20, 20, 0), c(0, 20, 20, 20, 0), c(0, 20, 20, 20, 0),
                             c(0, 20, 20, 20, 0), c(0, 20, 20, 20, 0), c(0, 20, 20, 20, 0),
                             c(0, 20, 20, 20, 0))),
                 n = I(list(rep(10, 5), rep(10, 5), rep(10, 5), c(6, 11, 11, 11, 11),
                            c(11, 11, 11, 11, 6), c(6, 11, 11, 11, 11),
                            c(11, 11, 11, 11, 6),
                            rep(10, 5), rep(10, 5), rep(10, 5), c(6, 11, 11, 11, 11),
                            c(11, 11, 11, 11, 6), c(6, 11, 11, 11, 11),
                            c(11, 11, 11, 11, 6),
                            rep(10, 5), rep(10, 5), rep(10, 5), c(6, 11, 11, 11, 11),
                            c(11, 11, 11, 11, 6), c(6, 11, 11, 11, 11),
                            c(11, 11, 11, 11, 6),
                            rep(10, 5), rep(10, 5), rep(10, 5), c(6, 11, 11, 11, 11),
                            c(11, 11, 11, 11, 6), c(6, 11, 11, 11, 11),
                            c(11, 11, 11, 11, 6))),
                 sigma = I(list(rep(30, 5), c(50, 10, 10, 10, 10), c(10, 10, 10, 10, 50),
                                c(10, 10, 10, 10, 50), c(10, 10, 10, 10, 50), c(50, 10, 10, 10, 10),
                                c(50, 10, 10, 10, 10),
                                rep(30, 5), c(50, 10, 10, 10, 10), c(10, 10, 10, 10, 50),
                                c(10, 10, 10, 10, 50), c(10, 10, 10, 10, 50), c(50, 10, 10, 10, 10),
                                c(50, 10, 10, 10, 10),
                                rep(30, 5), c(50, 10, 10, 10, 10), c(10, 10, 10, 10, 50),
                                c(10, 10, 10, 10, 50), c(10, 10, 10, 10, 50), c(50, 10, 10, 10, 10),
                                c(50, 10, 10, 10, 10),
                                rep(30, 5), c(50, 10, 10, 10, 10), c(10, 10, 10, 10, 50),
                                c(10, 10, 10, 10, 50), c(10, 10, 10, 10, 50), c(50, 10, 10, 10, 10),
                                c(50, 10, 10, 10, 10))),
                 direction = "lower", nrep = 1e5, alpha = 0.025)
n_arg <- nrow(arg)

# # Parallel
# library(future.apply)
# # plan(cluster)
# seed <- 10000
# result <- future_lapply(1:n_arg, FUN = sim, future.seed = seed,
#                         future.packages = c("mvtnorm"), arg = arg,
# future.scheduling = n_arg)
# results <- as.data.frame(do.call(rbind, result))
```

### Results for four treatment groups and control
```{r outputs four, echo=TRUE}
# $\mu_0=\mu_1=\mu_2=\mu_3=\mu_4=0$
results <- read.csv("/dunnett/simulation/four_treatment_groups.csv")
data_0_0_0_0_0 <- subset(results, mu_1 == 0 & mu_2 == 0 & mu_3 == 0,
                         select = -c(mu_0, mu_1, mu_2, mu_3, mu_4,
                                     n_0, n_1, n_2, n_3, n_4,
                                     sigma_0.2, sigma_1.2, sigma_2.2, sigma_3.2,
                                     sigma_4.2,
                                     nrep, alpha, time0, time1, time2, time3))
row.names(data_0_0_0_0_0) <- 1:nrow(data_0_0_0_0_0)
t(data_0_0_0_0_0) # $\mu_0=\mu_1=\mu_2=\mu_3=\mu_4=0$

# $\mu_0=\mu_2=\mu_3=\mu_4=0, \mu_1=20$
data_0_20_0_0_0 <- subset(results, mu_1 == 20 & mu_2 == 0 & mu_3 == 0,
                          select = -c(mu_0, mu_1, mu_2, mu_3, mu_4,
                                     n_0, n_1, n_2, n_3, n_4,
                                     sigma_0.2, sigma_1.2, sigma_2.2, sigma_3.2,
                                     sigma_4.2,
                                     nrep, alpha, time0, time1, time2, time3))
row.names(data_0_20_0_0_0) <- 1:nrow(data_0_20_0_0_0)
t(data_0_20_0_0_0) # $\mu_0=\mu_2=\mu_3=\mu_4=0, \mu_1=20$

# $\mu_0=\mu_3=\mu_4=0, \mu_1=\mu_2=20$
data_0_20_20_0_0 <- subset(results, mu_1 == 20 & mu_2 == 20 & mu_3 == 0,
                           select = -c(mu_0, mu_1, mu_2, mu_3, mu_4,
                                     n_0, n_1, n_2, n_3, n_4,
                                     sigma_0.2, sigma_1.2, sigma_2.2, sigma_3.2,
                                     sigma_4.2,
                                     nrep, alpha, time0, time1, time2, time3))
row.names(data_0_20_20_0_0) <- 1:nrow(data_0_20_20_0_0)
t(data_0_20_20_0_0) # $\mu_0=\mu_3=\mu_4=0, \mu_1=\mu_2=20$

# $\mu_0=\mu_4=0, \mu_1=\mu_2=\mu_3=20$
data_0_20_20_20_0 <- subset(results, mu_1 == 20 & mu_2 == 20 & mu_3 == 20,
                            select = -c(mu_0, mu_1, mu_2, mu_3, mu_4,
                                     n_0, n_1, n_2, n_3, n_4,
                                     sigma_0.2, sigma_1.2, sigma_2.2, sigma_3.2,
                                     sigma_4.2,
                                     nrep, alpha, time0, time1, time2, time3))
row.names(data_0_20_20_20_0) <- 1:nrow(data_0_20_20_20_0)
t(data_0_20_20_20_0) # $\mu_0=\mu_4=0, \mu_1=\mu_2=\mu_3=20$

data_time <- subset(results, select = -c(mu_0, mu_1, mu_2, mu_3, mu_4,
                                         n_0, n_1, n_2, n_3, n_4,
                                         sigma_0.2, sigma_1.2, sigma_2.2, sigma_3.2, sigma_4.2,
                                         nrep, alpha, 
                                         m0_fwer, m1_fwer, m2_fwer, m3_fwer))
round(colMeans(data_time), 4) # Mean computing time for each replication

sessionInfo()
```
